### 2014-06-06 related_work.tex
initial commit on related work

\paragraph{Object recognition with CNN}\label{object-recognition-with-cnn}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Alexnet \cite{Krizhevsky-NIPS-2012}
\item
  RCNN \cite{Girshick-CVPR-2014} and the couple other CNN detection methods \cite{Zou-CVPR-2014} \cite{Simonyan-ICLR-2014}.
\item
  Overfeat: explain dense evaluation \cite{Sermanet-ICLR-2014}
\end{itemize}

\paragraph{Cascaded detection}\label{cascaded-detection}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Viola Jones \cite{Viola2004}
\item
  Cascaded DPM \cite{Felzenszwalb-CVPR-2010}
\item
  \todo{Is there any CNN work?}
\end{itemize}

\paragraph{Dynamic selection}\label{dynamic-selection}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Timely Object Recognition \cite{Karayev-NIPS-2012}
\item
  Cross-talk cascades \cite{Dollar-ECCV-2012}
\item
  \todo{What else?}
\end{itemize}

>>>>

\paragraph{Object recognition with CNN}\label{object-recognition-with-cnn}
The recent success of deep convolutional neural networks (CNN) Alexnet \cite{Krizhevsky-NIPS-2012} on image classification tasks such as ImageNet \cite{deng2009cvpr} has spurred various investigations \cite{Girshick-CVPR-2014,Zou-CVPR-2014,Simonyan-ICLR-2014,Sermanet-ICLR-2014} how this success can be carried over to an detection task despite the prohibitive cost of evaluating such models densely in a naive manner. These previous attempts aim at reducing computational cost by reducing the search space of sliding window search by a bottom up window proposal scheme \cite{Girshick-CVPR-2014}, reducing computational overhead by sharing computation between windows to be evaluated \cite{Zou-CVPR-2014,Sermanet-ICLR-2014} as well as deriving a window sampling scheme that is based on the gradient of the network \cite{Simonyan-ICLR-2014}. All these method have in common that they rely on a fixed strategy and cannot adapt the computational scheme based on intermediate results, while we propose a dynamic scheme that steers computation based on intermediate outcomes in order to spend computation time most effectively.

\paragraph{Cascaded detection}\label{cascaded-detection}
Detection cascade \cite{Viola2004,Felzenszwalb-CVPR-2010} is a well established techniques to condition the computational scheme on intermediate outcomes based on a fixed evaluation order to features/classifiers. This idea has seen several refinements including sharing computation across cascades \cite{Dollar-ECCV-2012} and the possibility to skip evaluations \cite{benbouzid12icml}. Recently, a CNN with a cascaded structure for coarse to fine inference of facial feature points has been proposed \cite{cnn_cascade}. While previous cascade schemes really on a fixed ordering of evaluations, our scheme learns to traverse the available features/classifiers in arbitrary orders.

\paragraph{Dynamic selection}\label{dynamic-selection}
  Timely Object Recognition \cite{Karayev-NIPS-2012}
  Cross-talk cascades \cite{Dollar-ECCV-2012}
